### 2022-12-02 article/Conclusion.tex
Rename to article since there will be only 1 in this repo

\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps. In this way, reducing the numerous solutions to just one data window per source. After estimating the structural index (N = 3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}

>>>>

\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps. In this way, reducing the numerous solutions to just one data window per source. After estimating the structural index ($n = 3$) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}

### 2022-12-02 article/Result1.tex
Rename to article since there will be only 1 in this repo

\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$). Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}

>>>>

\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$). Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:SimpleSyntheic}.}
